Optimal Decomposition-Recombination Plans for 2D Well-Constrained Graphs

### 2014-12-05 doc/GMP2015/s01_introduction.tex
s01_introduction.tex edited online with Bitbucket

\subsection{Previous Work}
We now briefly survey existing techniques for studying 2D {\em qusecs,}  many of which are
{\it bar-joint} systems (Examples 1,2 above), {\it multibody-pin} systems (Example 4,5) or {\it pinned-line incidence} systems (Example 3). 
The limitations of these techniques directly motivate the contributions of this paper.

\medskip\noindent\underbar{{\sl (1) Finding (vertex)-maximal generically rigid subsystems}}
Fast, graph-based algorithms exist (pebble-game \cite{XX}),   
for locating all maximal, generically rigid subsystems \cite{XX}. 
When the input is rigid, these algorithms do nothing, i.e, the output is the same as the input.
However, both for self-similar or just aperiodic 2D qusecs, it is imperative to recursively decompose rigid systems 
into their rigid subsystems, down to the level of geometric primitives, in order to 
understand or design properties at all scales, such as: rigidity, flexes, distribution 
of external stresses as well as robustness/sensitivity to constraint variations.

@@

\subsection{Contributions}
\label{sec:cont}
In this paper, we  navigate the NP-hardness barrier mentioned in (2) above, for finding optimal DR-plans by defining a 
so-called {\it canonical} DR-plan and showing that all canonical DR-plans for isostatic 2D qusecs are optimal. 
We then give an efficient ($O(n^2)$) algorithm to find a canonical DR-plan for all 2DGMCS. The notion of a canonical DR-plan 
illuminates the essence of the NP-hardness of finding optimal DR-plans for overconstrained 2DGMCS and gives classes of 
overconstrained 2DGMCS for which the above  algorithm finds an optimal DR-plan. We then show how to judiciously combine 
existing methods for recombination, search of so-called, convex Cayley configuration spaces, and navigation of realizations, 
to explore a connected component of the configuration space of a flexible 2DGMCS, given a starting configuration. 
Software implementation can be found at: \todo{Provide Link}.

>>>>

\subsection{Previous Work on Relevant 2D Geometric Constraint Systems}
We now briefly survey existing techniques for studying 2D {\em qusecs,}  many of which are
{\it bar-joint} systems (Examples 1,2 above), {\it multibody-pin} systems (Example 4,5) or {\it pinned-line incidence} systems (Example 3). 
The limitations of these techniques directly motivate the contributions of this paper.

\medskip\noindent\underbar{{\sl (1) Finding (vertex)-maximal generically rigid subsystems}}
Fast, graph-based algorithms exist (pebble-game \cite{XX}),   
for locating all maximal, generically rigid subsystems \cite{XX}. 
When the input is rigid, these algorithms do nothing, i.e, the output is the same as the input.
However, both for self-similar or just aperiodic 2D qusecs, it is imperative to recursively decompose rigid systems 
into their rigid subsystems, down to the level of geometric primitives, in order to 
understand or design properties at all scales, such as: rigidity, flexes, distribution 
of external stresses,  well as robustness/sensitivity to constraint variations.

@@

\subsection{Contributions}
\label{sec:cont}
In this paper, we  navigate the NP-hardness barrier mentioned in (2) above, for finding optimal DR-plans by defining a 
so-called {\it canonical} DR-plan and showing a strong Church-Rosser property: {\it all canonical DR-plans for isostatic or underconstrained (independent) 
2D qusecs are optimal}. 
We then give an efficient ($O(n^2)$) algorithm to find a canonical (and hence optimal) DR-plan for all 3 types of 2D qusecs mentioned above.
canonical DR-plan 
illuminates the essence of the NP-hardness of finding optimal DR-plans for overconstrained  and gives classes of 
overconstrained 2DGMCS for which the above  algorithm finds an optimal DR-plan. We then show how to judiciously combine 
existing methods for recombination, search of so-called, convex Cayley configuration spaces, and navigation of realizations, 
to explore a connected component of the configuration space of a flexible 2DGMCS, given a starting configuration. 
Software implementation can be found at: \todo{Provide Link}.
